Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-06-21 GWLDCII.tex
fixed things about blocks A and B

Recall that $I_1$ determines the shape of the Le diagram: specifically, the elements of $I_1$ label the rows of the diagram, working from top right to bottom left. By the arguments in Lemma~\ref{lem I} we know that ${n,n-1,n-2, n-3 \not\in I_1^{V}}$ (which yields the leftmost four columns of the diagram for $V$) and that $I_1^{W} = I_1^{V}\cup \{n-3\}$. This implies that the right hand boundary of the shape of $V$ is the same as the right hand boundary of the shape of $W$ except that $W$ has one additional row of 3 boxes while $V$ has an additional column in the $n-3$ position; that is, an extra column fourth from the left. 
\sanote{Can we rephrase this in terms of row and column numbers (as in section 2) rather than use shape?}
\end{proof}

As illustrated in Figure~\ref{fig Le}, the pieces of the Le diagrams of $V$ and $W$ will be called $\mathcal{A}$ and $\mathcal{B}$ in what follows. \hlfix{Explicitly, $\mathcal(B)$ is the set of columns with labels $v < n-3$ and $\mathcal{A}$ the set of columns labeled by $n$, $n-1$ and $n-2$.}{is this accurate?} Over the course of the next few lemmas we will prove that the plusses in the $\mathcal{B}$ parts of each diagram are identical, and that the relationship between the plusses in the $\mathcal{A}$ regions can be described explicitly.

>>>>

Recall that $I_1$ determines the shape of the Le diagram: specifically, the elements of $I_1$ label the rows of the diagram, working from top right to bottom left. By the arguments in Lemma~\ref{lem I} we know that ${n,n-1,n-2, n-3 \not\in I_1^{V}}$ (which yields the leftmost four columns of the diagram for $V$) and that $I_1^{W} = I_1^{V}\cup \{n-3\}$. This implies that the right hand boundary of the shape of $V$ is the same as the right hand boundary of the shape of $W$ except that $W$ has one additional row of 3 boxes while $V$ has an additional column in the $n-3$ position; that is, an extra column fourth from the left. 
\end{proof}

As illustrated in Figure~\ref{fig Le}, the pieces of the Le diagrams of $V$ and $W$ will be called $\mathcal{A}$ and $\mathcal{B}$ in what follows. \hlfix{Explicitly, $\mathcal{B}$ is the set of columns with labels $v < n-3$ and $\mathcal{A}$ the set of columns labeled by $n$, $n-1$ and $n-2$ in $V$. In $W$, A consists of these columns without the last row.}{is this accurate?} Over the course of the next few lemmas we will prove that the plusses in the $\mathcal{B}$ parts of each diagram are identical, and that the relationship between the plusses in the $\mathcal{A}$ regions can be described explicitly.
